\newpage
\vspace*{0.5\baselineskip}
\begin{center}
\thispagestyle{empty}
\LARGE{\textbf{ACKNOWLEDGEMENTS}}\\[0.5cm]
\end{center}
% \vspace{0.05cm}
\doublespacing

We present with immense pleasure this work titled \textbf{``Smart Traffic Control System Using IoT"}. An endeavour over a long period can be successful with the advice and support of many well wishers.

We take this opportunity to express our gratitude and appreciation
to all of them. The satisfaction and euphoria that accompany the successful completion of any
task would be incomplete without mentioning the people who made it possible. So,
with gratitude we acknowledge all those whose guidance and encouragement made to
successfully complete this project.

We would like to express sincere thanks to our Principal \textbf{Dr. Pradeep S}, Malnad
College of Engineering for his encouragement made to successfully completion of the
project work. We wish to express our gratitude to \textbf{Dr.Geetha Kiran A}, Professor and Head, Department of Computer Science \& Engineering for providing a good working environment and for her constant support and encouragement.

It gives great pleasure in placing on record a deep sense of gratitude to our guide
\textbf{Mr. Shashidhara H V}, Associate Professor, Department of Computer Science \& Engineering for his daily evaluation of the work and for providing us constant encouragement with his unflinching support and valuable guidance throughout this project.

We would also like to thank all the staff of Computer Science and Engineering department who have directly or indirectly helped us in the completion of the project work. At last we would hereby acknowledge and thank our parents who have been a source of inspiration and also instrumental in the successful completion of the project work. \\

\large{\hspace*{3.5in} Hariharan K(4MC19CS050)}\\
\large{\hspace*{3.7in} Dhyan S Agni(4MC19CS043)}\\



% Salutations to our beloved and highly esteemed institute ``Malnad College Of Engineering" for having well qualified staff and labs furnished with necessary equipment.

% The successful completion of any task would be incomplete without mentioning the people who have constantly guided and inspired for the project and the report generation.

% We avail this opportunity to thank all those people who have helped us in the whole process of completion of this project and the report.

% We would like to express our deepest gratitude to our mentor {\textbf{Prof. Shashidhara H V}},Department of Computer Science and Engineering for his daily evaluation of the work and for providing us constant encouragement with his unflinching support and valuable guidance throughout this project. We are indebted to him as he has considered us worthy of this project and invested his faith in us. It was a great privilege to work under him. We will take away a lot more than just the technical knowledge from him.We would also like to place our special thanks to Dr.C V Venkatesh, Principal,Dr Geetha Kiran A,HOD Computer science and Engineering department and all Panel members Mr. Shashidhara H V(Panel Head),Associate Professor, Mr.Vasanth Kumar N.T,Assistant Professor, Mrs.Harshitha S, Assistant Professor and Mrs.Nivyashree R, Assistant Professor Malnad College of Engineering for providing the opportunity and the facilities for the completion of our project.\\



% Salutations to our beloved and highly esteemed institute ``Malnad College Of Engineering" for having well qualified staff and labs furnished with necessary equipment.

% The successful completion of any task would be incomplete without mentioning the people who have constantly guided and inspired for the project and the report generation.

% We avail this opportunity to thank all those people who have helped us in the whole process of completion of this project and the report.

% We would like to express our deepest gratitude to our mentor Mr. Shashidhara H V, Department of Computer Science \& Engineering for his daily evaluation of the work and for providing us constant encouragement with his unflinching support and valuable guidance throughout this project. We are indebted to him as he has considered us worthy of this project and invested his faith in us. It was a great privilege to work under him. We will take away a lot more than just the technical knowledge from him.

% We would also like to place our special thanks to Dr. C V Venkatesh, Principal, Malnad College Of Engineering for providing the opportunity and the facilities for the completion of our project. \\