\chapter{Introduction}

\section{Overview}
Smart traffic management system is an automated way of controlling and co ordinating the traffic in the city, in accordance with the real time traffic analytics, thus reducing the traffic congestion. In large Metropolitian cities, traffic congestion is a major problem. The congestion is caused due to number of factors like, increase in the number of vehicles that exceeds the capacity of the road, inefficient traffic management system, etc.

The current traffic management system is manual/preset and has a number of limitations, such as,
\begin{itemize}
\item Inability of the system to tackle the ever-increasing number of vehicles at a rapid rate.
\item Inefficient setup to co-ordinate vehicles like ambulances with minimum delay, through traffic, in case of emergencies.
\item Delay in the clearance of traffic due to rigid setup of the legacy systems, etc.
\end{itemize}

This IOT based smart traffic management system overcomes the flaws in the existing traffic management system, by means of providing an adaptive control of the traffic, with respect to the congestion at real time.

\pagebreak

\section{Problem Statement}
In the current traffic systems, the time for which the vehicles are allowed to pass through in a lane in the signal is fixed. This method is inefficient to handle the ever-growing traffic. Also, the traffic congestion of the cities is highly variable and unpredictable, which proves it difficult to preset these fixed timers of the traffic signals. Thus, it cannot handle the congestion of vehicles in the city, in an effective way. It can lead to waste of time when there is very low congestion and might build up the traffic during peak times.

Dipak K Dash \cite{trafficcongestion} has, it is estimated that, in our country, due to congestion, there is an annual loss of around \rupee60,000 crores which includes fuel wastage. Due to the traffic congestion, the average fuel mileage of a vehicle is only about 3.9kmpl and it also leads to wastage of time.

The proposed model is flexible and adaptive, which can handle these dynamic traffic trends. The model measures the current traffic of any given lane in real time and depending upon this value, it adjusts or adapts the time for which the green signal is to be turned ON/OFF, thereby ensuring smooth flow of vehicles, reducing congestion.

\section{Project Objective}
The core objective of the project is to implement a smart traffic management system, that reduces the traffic in large cities using IOT systems. The system measures the congestion of a given lane in real time and adjust accordingly the time period for which the green signal is to be turned on for that lane.

It also includes features like, prioritizing the movement of emergency vehicles like, ambulances, fire brigades, preventing the violation of traffic rules, etc. through various automation systems.

\pagebreak

\input{./literature-survey.tex} % adds the Literature Survey page

\section{Organization of Report}
This report is organized as follows,
\begin{itemize}
\item Chapter 1: Introduction - briefing about the overview, literature survey, problem formulation and methodology of the project.
\item Chapter 2: System Design – Explains the overall system architecture and the different components used in the system.
\item Chapter 3: Working principle and Procedure - It explains about the working principle of the project and the procedure to setup and run the model
\item Chapter 4: Result and Output – It consists of the summary of the results/output observed accompanied with pictures and associated discussions.
\item Chapter 5: Conclusion and Future Scopes – Finally, it is concluded with the project’s pros and cons, with the future possibilities in which the model can be improved.
\end{itemize}
